Typed Functional Genetic Programming

### 2013-11-11 tex/thesis.tex
[tex] article
[nic]
článek

Design goal behind our approach to crossover operation is
to try to generalize standard tree swapping mutation.
This is not because of dislike of more specialized crossovers;
it comes from systematic approach for exploring the domain of
typed functional GP --- thus I would like to start with the most common one.\\

@@

The difference between approach presented in this work and our approach 
may be stated in the following way. Approach presented in \cite{yo01}
tries to adopt some useful constructs from domain
of functional programming and use them for a benefit in problem solving by GP.
Whereas our approach is to perform genetic programming directly in the
simply typed lambda calculus.

>>>>

Design goal behind our approach to crossover operation is
to try to generalize standard tree swapping crossover.
This is not because of dislike of more specialized crossovers;
it comes from systematic approach for exploring the domain of
typed functional GP --- thus I would like to start with the most common one.\\

@@

The difference between approach presented in this work and our approach 
may be stated in the following way. Approach presented in \cite{yu01}
tries to adopt some useful constructs from domain
of functional programming and use them for a benefit in problem solving by GP.
Whereas our approach is to perform genetic programming directly in the
simply typed lambda calculus.
